---
title: "Exploratory Analysis"
author: "Andrew Wang, Sarah Huang, Joanna Phung, Kyle Dao"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, results = "hide")
source("mean_race_salaries.R")
source("difference_in_wage_by_gender.R")
source("poverty_by_race.R")
source("aggregate_table.R")
source("exploratory_analysis.R")
```

## Instructions (remove this before turning in):
- Write an introductory paragraph explaining the domain/data set (feel free to borrow from the project proposal)
- Write a summary paragraph that includes information calculated by your summary information function
- Render your table and describe pertinent observations found in it
- Describe the purpose of each chart (e.g., "this chart was intended to show the relationship between..."), render each chart, and describe pertinent observations found in each chart

## Introduction and Summary Information
[Intro paragraph goes here]

[Summary paragraph of the 5 variables go here] <br />
1. Mean Household Income per race in King County <br />
2. Change in Race Population Over Time <br />
3. Change in income per race <br />
4. Average difference in wage between males and females of similar occupation <br />
5. Race with the highest percentage in poverty <br />

## Our Aggregate Table
[Describe the purpose of the chart and pertinent chart observations]
```{r, echo=FALSE, results = 'asis', message=FALSE}
# install.packages("kableExtra")
library(kableExtra)
library(knitr)
kable(aggregate_table, "html") %>% kable_styling("striped") %>% scroll_box(width = "100%")
# kable(aggregate_table, caption = "Aggregate Salary and Population Data for each Race per Year")
```

## Average Salary per Race Chart
[Describe the purpose of the chart and pertinent chart observations]
```{r, echo=FALSE}
plot(mean_race_salaries)
```

## Poverty by Race Chart
[Describe the purpose of the chart and pertinent chart observations]
```{r, echo=FALSE}
plot(bar_plot)
```

## Difference in Wage by Gender
[Describe pertinent table observations]
```{r, echo=FALSE}
plot(avg_income)
```