---
title: "Assignment 3: Data Visualization of Incarceration"
author: "Andrew Wang, Sarah Huang, Joanna Phung, Kyle Dao"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, results = "hide")
source("mean_race_salaries.R")
source("difference_in_wage_by_gender.R")
source("poverty_by_race.R")
source("aggregate_table.R")
```

## Instructions (remove this before turning in):
Write an introductory paragraph explaining the domain/data set (feel free to borrow from the project proposal)
Write a summary paragraph that includes information calculated by your summary information function
Render your table and describe pertinent observations found in it
Describe the purpose of each chart (e.g., "this chart was intended to show the relationship between..."), render each chart, and describe pertinent observations found in each chart

## Introduction and Summary Information

 
## Our Aggregate Table
```{r, echo=FALSE}
aggregate_table
```

## Average Salary per Race Chart
```{r, echo=FALSE}
plot(mean_race_salaries)
```

## Poverty by Race Chart
```{r, echo=FALSE}
plot(bar_plot)
```

## Difference in Wage by Gender
```{r, echo=FALSE}
plot(avg_income)
```