---
title: "Exploratory Analysis"
author: "Andrew Wang, Sarah Huang, Joanna Phung, Kyle Dao"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, results = "hide")
source("mean_race_salaries.R")
source("difference_in_wage_by_gender.R")
source("poverty_by_race.R")
source("aggregate_table.R")
source("exploratory_analysis.R")
```

## Instructions (remove this before turning in):
- Write an introductory paragraph explaining the domain/data set (feel free to borrow from the project proposal)
- Write a summary paragraph that includes information calculated by your summary information function
- Render your table and describe pertinent observations found in it
- Describe the purpose of each chart (e.g., "this chart was intended to show the relationship between..."), render each chart, and describe pertinent observations found in each chart

## Introduction and Summary Information
Poverty is defined as "the state of being extremely poor". Across the US, low-income BIPOC communities have an increased risk of experiencing poverty in comparison to white middle-class families. Living in the U-District, our team has witnessed the ways in which poverty and low-income levels have affected houseless folx within our area. As a result, our project aims to analyze how factors such as household income, race, and gender impacts the poverty line. 

In reviewing all of our data, we can conclude that Native and Black folx have the lowest median and mean income within the King County area. 
[Summary paragraph of the 5 variables go here] <br />
1. Mean Household Income per race in King County <br />
2. Change in Race Population Over Time <br />
3. Change in income per race <br />
4. Average difference in wage between males and females of similar occupation <br />
5. Race with the highest percentage in poverty <br />

## Our Aggregate Table
Based on the data, we can identify that Native and Black folx have the lowest median income within King County. From 2019, their median income ranged from $60,000 - $68,000. In contrast, white and Asian folx have have the highest median income ranging from $104,000 - $118,000. The purpose of this chart is to allow us to see the racial disparities in income and poverty.

```{r, echo=FALSE, results = 'asis', message=FALSE}
# install.packages("kableExtra")
library(kableExtra)
library(knitr)
kable(aggregate_table, "html") %>% kable_styling("striped") %>% scroll_box(width = "100%")
# kable(aggregate_table, caption = "Aggregate Salary and Population Data for each Race per Year")
```

## Average Salary per Race Chart
The purpose of this chart is to allow us to see the average income per race in King County. In analyzing the statistics, we can conclude that Asians have the highest average income than Black folx. 

```{r, echo=FALSE}
plot(mean_race_salaries)
```

## Poverty by Race Chart
The purpose of this chart is to allow us to see the percentage of race population in poverty within the King County area. According to the Race Chart, we can see that white people have the highest percentage of poverty in comparison to BIPOC folx. While this may be the case, the dataset only shows the percentage of the total white population in poverty. 

[Describe the purpose of the chart and pertinent chart observations]
```{r, echo=FALSE}
plot(bar_plot)
```

## Difference in Wage by Gender
The purpose of this chart is to allow us to see the average wage for female and male workers from the same occupation. In analyzing the data, we can see that there is an income disparity and that male workers tend to get paid more by a significant amount. 

```{r, echo=FALSE}
plot(avg_income)
```